---
title: "Group 3 — Bodies and talk"
subtitle: "Studio wall"
author: "Group names here"
format:
  html:
    toc: true
    toc-depth: 2
---

# Spine

> How do bodies measure, how do people talk about mind and school, and how long do countries live?


```{r}
#1 label: setup
library(tidyverse)
library(ggformula)
library(skimr)
library(mosaic)
```



# Panel A — body / measure

*height_cm, weight_kg, waist_cm are Quant. sex is Qual.*

### 1. See the table

What is a case? Which columns are Quant / Qual? What is missing?

-we have 6 quantitative variables in our data - age, weight_kg, height_cm, waist_cm, hip_cm, chest_cm.
-we have 1 qualitative variable - sex.


> ## Read my Panel A CVS File.

```{r}
myPanelAData <- read_csv(file = "data/panel-A.csv")
```

```{r}
glimpse(myPanelAData)
skim(myPanelAData)

```

### 2. Ask

who is heavier between men and women ? what is the proportion of men and women ? how does waist size vary for men and women ? how does hip size vary for men and women ? how does chest size vary for men and women ? what are the age ranges in the given data set? what is the variation in chest size in the given data set? what is the variation in waist size in the given data set? what is the variation in hip size in the given data set? what is the variation in height in the given data set? what is the variation in weight in the given data set? who is taller between men and women? which sex has a larger variation in the age range?

### 3. Choose a mark

Who is heavier between men and women ? -Histogram

What is the proportion of men and women ? -Bar

How does waist size vary for men and women ? -Histogram

How does hip size vary for men and women ? -Density

How does chest size vary for men and women ? -Density

which sex has a larger variation in the age range in the given data-set ? -Histogram

Who is taller between men and women ? -Histogram

what are the age ranges in the given data set? -Bar

what is the variation in chest size in the given data set? -Density

what is the variation in waist size in the given data set? -Density

what is the variation in hip size in the given data set? -Density

what is the variation in height in the given data set? -Density

what is the variation in weight in the given data set? -Density

### 4. Predict

Referring to a stereotypical human anatomy, we predict that the variation in chest size and hip size would larger for women than men.

### 5. Make


Who is heavier between men and women ?

```{r}
myPanelAData |> gf_histogram(~weight_kg,fill =~sex,bins = 50)
```

What is the proportion of men and women ?

```{r}
myPanelAData |> gf_bar(~sex,fill=~sex)
```

How does waist size vary for men and women ?

```{r}
myPanelAData |> gf_histogram(~waist_cm,fill=~sex)
```

How does hip size vary for men and women ?

```{r}
myPanelAData |> gf_density(~hip_cm,fill=~sex)

```

How does chest size vary for men and women ?

```{r}
myPanelAData |> gf_density(~chest_cm,fill=~sex)
```

which sex has a larger variation in the age range in the given data-set ?

```{r}
myPanelAData |> gf_bar(~ age, fill = ~ sex)
```

Who is taller between men and women ?

```{r}
myPanelAData |> gf_histogram(~height_cm,fill =~sex,bins = 50)
```

what are the age ranges in the given data set?

```{r}
myPanelAData |> gf_bar(~ age)
```

what are the age ranges in the given data set?

```{r}
myPanelAData |> gf_density(~ weight_kg)
```

what is the variation in height in the given data set?

```{r}
myPanelAData |> gf_density(~ height_cm)
```

what is the variation in waist size in the given data set?

```{r}
myPanelAData |> gf_density(~ waist_cm)
```

what is the variation in hip size in the given data set?

```{r}
myPanelAData |> gf_density(~ hip_cm)
```

what is the variation in chest size in the given data set?

```{r}
myPanelAData |> gf_density(~ chest_cm)
```

### 6. Say

We all found the density graph comparing chest sizes of men and women interesting because according to the graph, men have a bigger chest size than women which is quite unexpected. Men also have larger variation in the sizes while women have more difference in density for different sizes. This is surprising because according to the bar graph, the ratio of women is slightly more than men, in comparison.
We also found the density graph comparing hip size of men and women surprising because it is contrasting the general belief that women have wider hips.

### 7. Limit

```{r}
myPanelAData |> group_by(sex) |> summarize (mean_chest_cm = mean(chest_cm,na.rm=T))
```

```{r}
mosaic::t_test(chest_cm ~ sex, data= myPanelAData)

```



# Panel B — category / talk

*degree × grass is Qual + Qual. mntlhlth is Quant — it belongs in a histogram or a grouped violin, not a mosaic.*

### 1. See the table

What is a case? Which columns are Quant / Qual? What is missing?

-we have 2 qualitative variables - degree [education] and grass [marijuana].
-we have 3 quantitative variables - mntlhlth [mental health], hrsl [hours of labour], hrsrelax [hours of relaxation]

```{r}
myPanelBData <- read_csv(file = "data/panel-B.csv")

```

```{r}

glimpse(myPanelBData)
skim(myPanelBData)

```

### 2. Ask

does the education of a person affect their opinion on whether marijuana should be legal or not?

### 3. Choose a mark

does the education of a person affect their opinion on whether marijuana should be legal or not? - mosaic graph

### 4. Predict

we predict that a person pursuing a higher education degree would want marijuana to be legal, to regulate stress levels and mental health.

### 5. Make

modifying

```{r}
 myPanelBData_mod <- myPanelBData |> drop_na(grass)
```

```{r}
dim(myPanelBData_mod)
```

making

```{r}
 vcd::structable(degree~grass,data=myPanelBData)
```


```{r}
vcd::structable(degree~grass, data=myPanelBData) |>
  vcd::mosaic(labeling_args = list(rot_labels = c(top = 45)),
              margins = c(top = 6))
```
```{r}
vcd::structable(degree~grass, data=myPanelBData) |>
  vcd::mosaic(type="expected", labeling_args = list(rot_labels = c(top = 45)),
              margins = c(top = 6))
```

### 6. Say

Looking at the graph, the ratio of people who think marijuana should be legal and not legal appears to be similar, in each individual degree. 
Saying that, it is surprising information to see that the percentage of high schoolers who want marijuana to be legal is way larger than any other degrees. This could also be because the number of high schoolers in this data set is more.

### 7. Limit

```{r}
mosaic::xchisq.test(degree~grass, data=myPanelBData)
```



# Panel C — place

*lifeExp is the honest fill. pop is a count — symbol map, not choropleth.*

Geometry is not in the CSV. Join in R, then use the same seven headings.

``` r
# library(sf)
# library(rnaturalearth)
# world <- ne_countries(scale = "medium", returnclass = "sf")
# # join on country name; list the unmatched labels
```

### 1. See the table

What is a case? Which columns are Quant / Qual? What is missing?

``` r
# glimpse() / inspect() / skim()
```

### 2. Ask

One question *this* table can answer. One it cannot. Write both.

### 3. Choose a mark

Geom, map mark, or (later) test that matches the pair type. Name it before you code.

### 4. Predict

What do we think we will see? One sentence, before Run.

### 5. Make

Human brick first. Optional: one AI prompt, pasted below, only for what section 3 named.

``` r
# human chunk

# ## Prompt we actually used
# ai_draft
# ours
```

### 6. Say

Caption + one sentence we will stand behind. Title is a sentence, not a column name.

### 7. Limit

What this panel cannot do. Which kit table we refused to abuse.

# Conclusion

What the spine looks like after three panels.

- The question we will defend in ninety seconds
- What we will **not** claim
- Which lines were human, which were machine
- Limits: sample, missingness, the test we did not run
- Gift for the steal-this strip (palette, annotation, join trick)

``` r
# sessionInfo()
```
